\LARGE \bf Steering a Swarm Using Global Inputs And Swarm Statistics

### 2016-08-09 journalSwarmControl/expResults.tex
added captions

We compared attractive and repulsive control with the global control used for the other experiments. The attractive and repulsive controllers were loosely modeled after scanning tunneling microscopes (STM), but also apply to magnetic manipulation, e.g. \cite{Khalil2013} and biological models, e.g. \cite{goodrich2012types}. STMs can be used to arrange atoms and make small assemblies~\cite{avouris1995manipulation}. An STM tip is charged with electrical potential, and used to repel like-charged or to attract differently-charged molecules. In contrast, the global controller uses a uniform field (perhaps formed by parallel lines of differently-charged conductors) to pull molecules in the same direction.
The experiment challenged players to assemble a three-block pyramid with a swarm of 16 robots.

>>>>

We compared attractive and repulsive control with the global control used for the other experiments. The attractive and repulsive controllers were loosely modeled after scanning tunneling microscopes (STM), but also apply to magnetic manipulation, e.g.\ \cite{Khalil2013} and biological models, e.g. \cite{goodrich2012types}. STMs can be used to arrange atoms and make small assemblies~\cite{avouris1995manipulation}. An STM tip is charged with electrical potential, and used to repel like-charged or to attract differently-charged molecules. In contrast, the global controller uses a uniform field (perhaps formed by parallel lines of differently-charged conductors) to pull molecules in the same direction.
The experiment challenged players to assemble a three-block pyramid with a swarm of 16 robots.

### 2016-08-09 journalSwarmControl/experiment.tex
added captions

 A corresponding reward function gives a high reward to the goal state,  
 a large negative reward to states including obstacles, and a small negative reward to all other states.
The reward function $r(x,u)$ is defined as
\begin{align}
r(x,u) &=  \left\{
\begin{array}{ll}
     +100, &  \textrm{if } u \textrm{ leads to goal state}\\
      -100, & \textrm{if } u \textrm{ leads to a state with an obstacle} \\
      -1, & \textrm{otherwise}\\
\end{array} 
\right.
\end{align}
where $u$ is the action and $x$ is the current state. 
  Value iteration iteratively learns the value $\hat{V}(x)$ for the object being in each state $x$. The optimal policy is the control action that, in probability, results in the largest value:
   \begin{align} \nabla \mathbf{M_{MDP}}= \arg\max_u   [ r(x,u) + \sum\limits_{j=1}^N \hat{V}(x_j) p(x_j| u,x)].  \label{eq:OptimalPolicy}
   \end{align}
   The value function $\hat{V}(x_j) $ is calculated by computing the value $\hat{V}$ for all $N$ states and iterating until convergence:
\begin{align}
\text{for }&\text{$i=1$ to $N$ do} \nonumber \\
&\hat{V} (x_j) = \gamma \max_u [r(x_j,u) + \sum\limits_{i=1}^N \hat{V}(x_i) p(x_i| u,x_j)] \label{eq:ValueIteration}\\
\text{end}& \nonumber
\end{align}
In our experiments $\gamma = 0.97$, and \eqref{eq:ValueIteration} was iterated 200 times. A {\sc Matlab} implementation of this algorithm is available at \href{https://www.mathworks.com/matlabcentral/fileexchange/49992-mdp-robot-grid-world-example}{\emph{MDP grid world example}}.%\todo{link to algorithm}.  
%Rather than a shortest distance to goal, $\nabla \mathbf{M}_{MDP}$  gives the approximate minimum cost to goal.

$\mathbf{M}_{BFS}$ and the value function are shown in Fig.~\ref{fig:BFSGradient}. 
In 10 simulations with 100 robots, pushing the object to goal using $\mathbf{M}_{BFS}$ required $\mu=183, \sigma=179$ s while  $\mathbf{M}_{MDP}$ required $\mu=90, \sigma=35$ s.
%\todo{(report results of 10 simulations with BFS and with PI.  Give mean and std)}

@@

\subsection{Algorithm for object manipulation}
 We use the hybrid hysteresis-based controller in Alg.~\ref{alg:MeanVarianceControl}  to track the desired position, while maintaining sufficient robot density to move the object by switching to minimize variance whenever variance exceeds a set limit. The minimize variance control law \eqref{eq:PDcontrolVariance} is slightly modified to choose the nearest corner further from the goal than $\mathbf{b}$ with an obstacle-free straight-line path to $\mathbf{b}$. A timer is also used to monitor the mean position of the swarm to know if the swarm is stuck in one of the corners. It gives the previous corner when the swarm is stuck to change the swarm's configuration and getting out of that local minimum. 
The control algorithm  for object manipulation is listed in Alg.~\ref{alg:BlockPushing}.

\todo{add the timeout function: I added two lines.}

@@

The interaction between the robots and object is impulsive so, like the study of impulsive pulling in  \cite{christensen2016let},  adding additional robots decreases completion time, but with diminishing returns. 
 After 75 robots, additional robots no longer can interact with the object and do not contribute to the task success. 
Brownian noise adds stochasticity.  This randomness can break the object free if it is stuck, but diminishes the effect of the control input.  Large amounts of noise increase completion time.
The robots have limited force, so increasing the object weight increases completion time.  
 Rectangles and squares tend to get stuck in the 90$^\circ$ workspace corners, and cause longer completion times than circles and hexagons.

>>>>

 A corresponding reward function gives a high reward to the goal state,  
 a large negative reward to states including obstacles, and a small negative reward to all other states.
The reward function $r(x,u)$ is defined as
\begin{align}
r(x,u) &=  \left\{
\begin{array}{ll}
     +100, &  \textrm{if } u \textrm{ leads to goal state}\\
      -100, & \textrm{if } u \textrm{ leads to a state with an obstacle} \\
      -1, & \textrm{otherwise}\\
\end{array} 
\right.
\end{align}
where $u$ is the action and $x$ is the current state. 
  Value iteration iteratively learns the value $\hat{V}(x)$ for the object being in each state $x$. The optimal policy is the control action that, in probability, results in the largest value:
   \begin{align} \nabla \mathbf{M_{MDP}}(x) = \arg\max_u   [ r(x,u) + \sum\limits_{j=1}^N \hat{V}(x_j) p(x_j| u,x)].  \label{eq:OptimalPolicy}
   \end{align}
   The value function $\hat{V}(x_j) $ is calculated by computing the value $\hat{V}$ for all $N$ states and iterating until convergence:
\begin{align}
\text{for }&\text{$i=1$ to $N$ do} \nonumber \\
&\hat{V} (x_j) = \gamma \max_u [r(x_j,u) + \sum\limits_{i=1}^N \hat{V}(x_i) p(x_i| u,x_j)] \label{eq:ValueIteration}\\
\text{end}& \nonumber
\end{align}
In our experiments $\gamma = 0.97$, and \eqref{eq:ValueIteration} was iterated 200 times. A {\sc Matlab} implementation of this algorithm is available at \href{https://www.mathworks.com/matlabcentral/fileexchange/49992-mdp-robot-grid-world-example}{\emph{MDP grid world example}}.%\todo{link to algorithm}.  
%Rather than a shortest distance to goal, $\nabla \mathbf{M}_{MDP}$  gives the approximate minimum cost to goal.

$\mathbf{M}_{BFS}$ and the value function are shown in Fig.~\ref{fig:BFSGradient}. 
In 10 simulations with 100 robots, pushing the object to goal using BFS required a mean and standard deviation of $183\pm 179$ s while Policy Iteration required $90\pm 35$ s.
%\todo{(report results of 10 simulations with BFS and with PI.  Give mean and std)}

@@

\subsection{Algorithm for object manipulation}
 We use the hybrid hysteresis-based controller in Alg.~\ref{alg:MeanVarianceControl}  to track the desired position, while maintaining sufficient robot density to move the object by switching to minimize variance whenever variance exceeds a set limit. The minimize variance control law \eqref{eq:PDcontrolVariance} is slightly modified to choose the nearest corner further from the goal than $\mathbf{b}$ with an obstacle-free straight-line path to $\mathbf{b}$. 
The control algorithm  for object manipulation is listed in Alg.~\ref{alg:BlockPushing}.

In rare cases during simulations the swarm may become trapped in a local minima of \eqref{eq:potentialfield}.
If the swarm mean position does not change for ten seconds, the swarm is assumed to be in a local minima and is commanded to move toward the previous corner. As soon as the mean position changes, normal control resumes.

%\todo{add the timeout function: I added two lines.}

@@

The interaction between the robots and object is impulsive so, like the study of impulsive pulling in  \cite{christensen2016let},  adding additional robots decreases completion time, but with diminishing returns. 
 After 75 robots, additional robots no longer can interact with the object and do not contribute to the task success. 
Brownian noise adds stochasticity.  This randomness can break the object free if it is stuck, but diminishes the effect of the control input.  
 Increasing noise increases completion time. 
 Large amounts of noise caused failures, defined as trials lasting longer than 1000s.  With $W=50$, XX of 20 trials failed.  With $W=100$, XX of 20 trials failed.
The robots have limited force, so increasing the object weight increases completion time.  
Each shape was designed to have the same mass and area.
 Rectangles and squares tend to get stuck in the 90$^\circ$ workspace corners, and cause longer completion times than circles, triangles, and hexagons.

### 2016-08-09 journalSwarmControl/realExperiment.tex
added captions

The objects were 3D printed from ABS plastic. Laser-cut patterns for the neon green fiducial markers on the robots and {\sc Matlab} tracking code are available at our github repository~\cite{Shahrokhi2015GitHubShapeControl}.
\begin{figure*}
\begin{center}
	%\includegraphics[width=0.5\columnwidth]{SetUp.pdf}
	\begin{overpic}[width=0.6\columnwidth]{SetUp.pdf}%\put(1,75){a)}
	\end{overpic}\\
	\begin{overpic}[width=0.35\columnwidth]{AllShapesR.pdf}%\put(5,85){b)}
	\end{overpic}
	\begin{overpic}[width=0.35\columnwidth]{PotentialExp.pdf}%\put(5,85){c)}
	\end{overpic}

\end{center}

\caption{\label{fig:setup}
(Top)Hardware platform:  table with 1.5$\times$1.2 m workspace, surrounded by four remotely triggered 30W LED and four 50W LED floodlights, with an overhead machine vision system. (Down left) A swarm of robots, all controlled by a uniform force field, can be effectively controlled by a hybrid controller that knows only the first and second moments of the robot distribution. Here is a swarm of hardware robots (kilobots) that pushes a green object with different shapes toward the goal. (Down right) The potential fields view in hardware experiments. See video attachment~\cite{ShivaVideo2015}
}
\end{figure*}

@@

The kilobots performed five successful runs of object manipulation through the obstacle maze.
Each trial used 100 kilobots. Videos of each are in the multimedia extension. Trials two-five were performed in a row with no failures in between.  For each trial, fully charged kilobots were placed in the lower left-hand of the workspace, as shown in Fig.~\ref{fig:expSnapShot}.  The moveable object was placed in the lower center of the workspace. The same controller as in the simulation, Alg.~\ref{alg:BlockPushing}, but with discretized control inputs, was coded in {\sc Matlab}.  Trials were run until the object COM entered the goal region.  The trials ran for \{24:25, 57:37, 50:00, 36:02, 45:07\} (minutes:seconds).  This is a mean of \{42:38\} (minutes:seconds) and a standard deviation of \{12:51\}(minutes:seconds). Also there was a trial with the circular object for \{52:35 \} (minutes:seconds). Another trial with square like object ran for \{114:31 \} (minutes:seconds). We also tried triangular object for \{ XX:YY \} (minutes:seconds).

>>>>

The Laser-cut patterns for the neon green fiducial markers on the robots and {\sc Matlab} tracking code are available at our github repository~\cite{Shahrokhi2015GitHubShapeControl}. 
The objects were 3D printed from ABS plastic with a paper overlay. 
Shapes included a 325 cm$^2$ equilateral triangle, 
%Small Equilateral Triangle 140 cm$^2$,
 324 cm$^2$ square,
 281 cm$^2$ hexagon,
254 cm$^2$ circle, 
and a 486 cm$^2$ (18 cm$\times$27 cm)  rectangle.

\begin{figure*}
\begin{center}
	%\includegraphics[width=0.5\columnwidth]{SetUp.pdf}
	\begin{overpic}[width=0.6\columnwidth]{SetUp.pdf}%\put(1,75){A}
	\end{overpic}\\
	\begin{overpic}[width=0.35\columnwidth]{AllShapesR.pdf}%\put(-0,85){B}
	\end{overpic}
	\begin{overpic}[width=0.35\columnwidth]{PotentialExp.pdf}%\put(-0,85){C}
	\end{overpic}
\end{center}

\caption{\label{fig:setup}
(Top) Hardware platform. (Lower left) Four shapes used for hardware experiments. (Lower right) Visualization of potential field. }
\end{figure*}

@@

The kilobots performed five successful runs of object manipulation through the obstacle maze.
Each trial used 100 kilobots. Videos of each are in the multimedia extension. Trials two-five were performed in a row with no failures in between.  For each trial, fully charged kilobots were placed in the lower left-hand of the workspace, as shown in Fig.~\ref{fig:expSnapShot}.  The moveable object was placed in the lower center of the workspace. The same controller as in the simulation, Alg.~\ref{alg:BlockPushing}, but with discretized control inputs, was coded in {\sc Matlab}.  Trials were run until the object COM entered the goal region.  The trials ran for \{24:25, 57:37, 50:00, 36:02, 45:07\} minutes.  This is a mean of 42:38 and a standard deviation of 12:51 minutes. 
A circular object completed in 52:35 minutes. 
A square object completed in 114:31 minutes. 
A triangular object completed in XX:YY minutes.
